Beta to Release Matching: Modeling

### 2020-03-11 poc/matchIt/modeling.Rmd
updating the model selection

```{r}
# downsampling
df_1x_sm <- df_1x %>% sample_n(size = 70000)
df_2x_sm <- df_2x %>% sample_n(size = 70000)
df_4x_sm <- df_4x %>% sample_n(size = 70000)
```

```{r}
f <- freq(as.factor(df_1x_sm$label_beta)) # ~ 50% - 50%
f <- freq(as.factor(df_2x_sm$label_beta)) # ~ 70% - 30%
f <- freq(as.factor(df_4x_sm$label_beta)) # ~ 80% - 20%
```

@@

```{r}
engagement <- c('active_hours','active_hours_max','uri_count','uri_count_max','search_count','search_count_max','num_pages','num_pages_max','daily_max_tabs','daily_max_tabs_max','daily_unique_domains','daily_unique_domains_max','daily_tabs_opened','daily_tabs_opened_max')

@@

```{r}
exp_1 <- c('daily_num_sessions_started', 'daily_num_sessions_started_max', 'FX_PAGE_LOAD_MS_2_PARENT', 'fxa_configured_True', 'memory_mb', 'num_active_days', 'num_addons', 'num_bookmarks', 'profile_age','session_length','session_length_max','TIME_TO_DOM_COMPLETE_MS','TIME_TO_DOM_CONTENT_LOADED_END_MS','TIME_TO_DOM_INTERACTIVE_MS','TIME_TO_LOAD_EVENT_END_MS','TIME_TO_NON_BLANK_PAINT_MS','timezone_cat_0_2')

@@

```{r}
exp_5  <- c(setdiff(names(cov_df_1x[3:73]), engagement))
exp_6  <- c(setdiff(names(cov_df_2x), engagement)) 
exps <- list(exp_1 = exp_1, exp_2 = exp_2, exp_3 = exp_3, exp_4 = exp_4, exp_5 = exp_5, exp_6 = exp_6)
```

@@

```{r, collapse=TRUE}
ps_1x <- list()
for (exp in names(exps)){
  ps <- glm(generate_formula(exps[[exp]], label), data=df_1x_sm, family=binomial())
  ps_1x[[exp]] <- ps
  print(summary(ps))
}
```

@@

```{r, collapse=TRUE}
ps_2x <- list()
for (exp in names(exps)){
  ps <- glm(generate_formula(exps[[exp]], label), data=df_2x_sm, family=binomial())
  ps_2x[[exp]] <- ps
  print(summary(ps))
}
```

@@

```{r, collapse=TRUE}
ps_4x <- list()
for (exp in names(exps)){
  ps <- glm(generate_formula(exps[[exp]], label), data=df_4x_sm, family=binomial())
  ps_4x[[exp]] <- ps
  print(summary(ps))
}
```

@@

```{r, collapse=TRUE}
cem_results_1x <- list()
cem_models_1x <- list()
for (exp in names(exps)){
  cem <- matchit(formula = generate_formula(exps[[exp]], label), df_1x_sm, 'cem')
  res <- match.data(cem)
  cem_models_1x[[exp]] <- cem
  cem_results_1x[[exp]] <- res
  #print(summary(cem))
}
```

@@

```{r, collapse=TRUE}
cem_results_2x <- list()
cem_models_2x <- list()
for (exp in names(exps)){
  cem <- matchit(formula = generate_formula(exps[[exp]], label), df_2x_sm, 'cem')
  res <- match.data(cem)
  cem_models_2x[[exp]] <- cem
  cem_results_2x[[exp]] <- res
  #print(summary(cem))
}
```

@@

```{r, collapse=TRUE}
cem_results_4x <- list()
cem_models_4x <- list()
for (exp in names(exps)){
  cem <- matchit(formula = generate_formula(exps[[exp]], label), df_4x_sm, 'cem')
  res <- match.data(cem)
  cem_models_4x[[exp]] <- cem
  cem_results_4x[[exp]] <- res
  #print(summary(cem))
}
```

@@

```{r, collapse=TRUE}
nn_results_1x <- list()
nn_models_1x <- list()
for (exp in names(exps)){
  nn <- matchit(formula = generate_formula(exps[[exp]], label), df_1x_sm, 'nearest', replace = TRUE)
  res <- match.data(nn)
  nn_models_1x[[exp]] <- nn
  nn_results_1x[[exp]] <- res
  #print(summary(nn))
}
```

@@

```{r, collapse=TRUE}
nn_results_2x <- list()
nn_models_2x <- list()
for (exp in names(exps)){
  nn <- matchit(formula = generate_formula(exps[[exp]], label), df_2x_sm, 'nearest', replace = TRUE)
  res <- match.data(nn)
  nn_models_2x[[exp]] <- nn
  nn_results_2x[[exp]] <- res
  #print(summary(nn))
}
```

@@

```{r, collapse=TRUE}
nn_results_4x <- list()
nn_models_4x <- list()
for (exp in names(exps)){
  nn <- matchit(formula = generate_formula(exps[[exp]], label), df_4x_sm, 'nearest', replace = TRUE)
  res <- match.data(nn)
  nn_models_4x[[exp]] <- nn
  nn_results_4x[[exp]] <- res
  #print(summary(nn))
}
```

### Match using CEM: Full

```{r, collapse=TRUE}
cem_full_results_1x <- list()
cem_full_models_1x <- list()
for (exp in names(exps)){
  nn <- matchit(formula = generate_formula(exps[[exp]], label), df_1x, 'cem')
  res <- match.data(nn)
  cem_full_models_1x[[exp]] <- nn
  cem_full_results_1x[[exp]] <- res
  #print(summary(nn))
}
```

```{r, collapse=TRUE}
cem_full_results_2x <- list()
cem_full_models_2x <- list()
for (exp in names(exps)){
  nn <- matchit(formula = generate_formula(exps[[exp]], label), df_2x, 'cem')
  res <- match.data(nn)
  cem_full_models_2x[[exp]] <- nn
  cem_full_results_2x[[exp]] <- res
  #print(summary(nn))
}
```

```{r, collapse=TRUE}
cem_full_results_4x <- list()
cem_full_models_4x <- list()
for (exp in names(exps)){
  nn <- matchit(formula = generate_formula(exps[[exp]], label), df_4x, 'cem')
  res <- match.data(nn)
  cem_full_models_4x[[exp]] <- nn
  cem_full_results_4x[[exp]] <- res
  #print(summary(nn))
}
```

@@

##### CEM: Full Dataset

```{r fig.height=7, fig.width=14}
par(mfrow=c(2,3))
for (m.cem in cem_full_models_1x){
  plot(m.cem, type = "hist", col = "#111d5e")
}
```

```{r fig.height=7, fig.width=14}
par(mfrow=c(2,3))
for (m.cem in cem_full_models_2x){
  plot(m.cem, type = "hist", col = "#611e62")
}
```

```{r fig.height=7, fig.width=14}
par(mfrow=c(2,3))
for (m.cem in cem_full_models_4x){
  plot(m.cem, type = "hist", col = "#b21f66")
}
```

@@

```{r fig.height=7, fig.width=14}
plot(nn_models_1x$exp_3, type = "QQ", col = "#111d5e")
```

```{r fig.height=7, fig.width=14}
plot(nn_models_1x$exp_4, type = "QQ", col = "#111d5e")
```

* Control unit quantile values are plotted on the x-axis, and treated unit quantile values are plotted on the y-axis. If values fall below the 45 degree line, control units generally take lower values of the covariate.

* Data points that fall exactly on the 45 degree line indicate that the marginal distributions are identical, that is, the empirical distributions are the same in the treated and control groups.

* Deviations from the 45 degree line indicate differences in the empirical distribution. Therefore, despite the promising results of the previous analysis, we still have some variables with different distributions after matching.

@@

>>>>

```{r echo=TRUE}
# downsampling
df_1x_sm <- df_1x %>% sample_n(size = 70000)
df_2x_sm <- df_2x %>% sample_n(size = 70000)
df_4x_sm <- df_4x %>% sample_n(size = 70000)
```

```{r}
f <- freq(as.factor(df_1x_sm$label_beta)) # ~ 50% - 50%
print(paste('50% - 50%'))

f <- freq(as.factor(df_2x_sm$label_beta)) # ~ 70% - 30%
print(paste('70% - 30%'))

f <- freq(as.factor(df_4x_sm$label_beta)) # ~ 80% - 20%
print(paste('80% - 20%'))
```

@@

```{r echo=TRUE}
engagement <- c('active_hours','active_hours_max','uri_count','uri_count_max','search_count','search_count_max','num_pages','num_pages_max','daily_max_tabs','daily_max_tabs_max','daily_unique_domains','daily_unique_domains_max','daily_tabs_opened','daily_tabs_opened_max')

@@

```{r echo=TRUE}
exp_1 <- c('daily_num_sessions_started', 'daily_num_sessions_started_max', 'FX_PAGE_LOAD_MS_2_PARENT', 'fxa_configured_True', 'memory_mb', 'num_active_days', 'num_addons', 'num_bookmarks', 'profile_age','session_length','session_length_max','TIME_TO_DOM_COMPLETE_MS','TIME_TO_DOM_CONTENT_LOADED_END_MS','TIME_TO_DOM_INTERACTIVE_MS','TIME_TO_LOAD_EVENT_END_MS','TIME_TO_NON_BLANK_PAINT_MS','timezone_cat_0_2')

@@

```{r echo=TRUE}
exp_5  <- c(setdiff(names(cov_df_1x[3:73]), engagement))
exp_6  <- c(setdiff(names(cov_df_2x), engagement)) 
exps <- list(exp_1 = exp_1, exp_2 = exp_2, exp_3 = exp_3, exp_4 = exp_4, exp_5 = exp_5, exp_6 = exp_6)
```

@@

```{r message=FALSE, warning=FALSE}
ps_1x <- list()
for (exp in names(exps)){
  ps <- glm(generate_formula(exps[[exp]], label), data=df_1x_sm, family=binomial())
  ps_1x[[exp]] <- ps
  print(paste(exp))
  print(summary(ps))
}
```

@@

```{r message=FALSE, warning=FALSE}
ps_2x <- list()
for (exp in names(exps)){
  ps <- glm(generate_formula(exps[[exp]], label), data=df_2x_sm, family=binomial())
  ps_2x[[exp]] <- ps
  print(paste(exp))
  print(summary(ps))
}
```

@@

```{r message=FALSE, warning=FALSE}
ps_4x <- list()
for (exp in names(exps)){
  ps <- glm(generate_formula(exps[[exp]], label), data=df_4x_sm, family=binomial())
  ps_4x[[exp]] <- ps
  print(paste(exp))
  print(summary(ps))
}
```

@@

```{r message=FALSE, warning=FALSE}
cem_results_1x <- list()
cem_models_1x <- list()
for (exp in names(exps)){
  cem <- matchit(formula = generate_formula(exps[[exp]], label), df_1x_sm, 'cem')
  res <- match.data(cem)
  cem_models_1x[[exp]] <- cem
  cem_results_1x[[exp]] <- res
  #print(summary(cem))
}
```

@@

```{r message=FALSE, warning=FALSE}
cem_results_2x <- list()
cem_models_2x <- list()
for (exp in names(exps)){
  cem <- matchit(formula = generate_formula(exps[[exp]], label), df_2x_sm, 'cem')
  res <- match.data(cem)
  cem_models_2x[[exp]] <- cem
  cem_results_2x[[exp]] <- res
  #print(summary(cem))
}
```

@@

```{r message=FALSE, warning=FALSE}
cem_results_4x <- list()
cem_models_4x <- list()
for (exp in names(exps)){
  cem <- matchit(formula = generate_formula(exps[[exp]], label), df_4x_sm, 'cem')
  res <- match.data(cem)
  cem_models_4x[[exp]] <- cem
  cem_results_4x[[exp]] <- res
  #print(summary(cem))
}
```

@@

```{r message=FALSE, warning=FALSE}
nn_results_1x <- list()
nn_models_1x <- list()
for (exp in names(exps)){
  nn <- matchit(formula = generate_formula(exps[[exp]], label), df_1x_sm, 'nearest', replace = TRUE)
  res <- match.data(nn)
  nn_models_1x[[exp]] <- nn
  nn_results_1x[[exp]] <- res
  #print(summary(nn))
}
```

@@

```{r message=FALSE, warning=FALSE}
nn_results_2x <- list()
nn_models_2x <- list()
for (exp in names(exps)){
  nn <- matchit(formula = generate_formula(exps[[exp]], label), df_2x_sm, 'nearest', replace = TRUE)
  res <- match.data(nn)
  nn_models_2x[[exp]] <- nn
  nn_results_2x[[exp]] <- res
  #print(summary(nn))
}
```

@@

```{r message=FALSE, warning=FALSE}
nn_results_4x <- list()
nn_models_4x <- list()
for (exp in names(exps)){
  nn <- matchit(formula = generate_formula(exps[[exp]], label), df_4x_sm, 'nearest', replace = TRUE)
  res <- match.data(nn)
  nn_models_4x[[exp]] <- nn
  nn_results_4x[[exp]] <- res
  #print(summary(nn))
}
```

@@

@@

@@

# Saving

```{r}
save(list=c("df_1x","df_1x_sm","exp_3","exp_4"), file="modeling.RData")
```
